---
title: "Kermit Perceptions Rank-Based Test"
author: "Sandro Lallas"
date: "11/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Sandro's first message in the document.

Yo wassuppppp

just tryna make a dollar out of 50 cents

```{r}
library(tidyverse)
kermit <- read_csv("kermit.csv")
```

```{r}
#Side by side histograms of the Score.pre for all respondents, separated by the gender column

kermit_hist <- ggplot(kermit, aes(x = Score.pre ))+ 
  geom_histogram(bins = 4)+
  facet_wrap(~Gender)
kermit_hist
```

Creator: Perform rank-based comparisons using Mann_Whitney U and Wilcoxon-Signed Rank

Question: Is there a significant difference in pre-talk ranks of Kermit for Male and Female respondents?

```{r}

mwu_kermit <- kermit %>%
  wilcox.test(Score.pre ~ Gender, data = .)

# Null hypothesis: There is NOT a significant difference in ranks for male and female respondents

# Alterntive: There is a significant difference in ranks

mwu_kermit

```

"There was no significant difference in ranks for male and female respondents (W = 155.5, p = 0.4, alpha = 0.05)."